\begin{thebibliography}{9}

	\bibitem{domo}
	\hypertarget{domo}{} 
	Data never sleeps 6.0
	\\\texttt{\url{https://www.domo.com/learn/data-never-sleeps-6}}
	
	\bibitem{finder}
	\hypertarget{finder}{} 
	Netflix International: What movies and TV shows can I watch, and where can I watch them?
	\\\texttt{\url{https://www.finder.com/global-netflix-library-totals}}

	\bibitem{scrapehero}
	\hypertarget{scrapehero}{} 
	How Many Products Does Amazon Sell? – April 2019
	\\\texttt{\url{https://www.scrapehero.com/number-of-products-on-amazon-april-2019/}}
	
	\bibitem{ErionCanoMaurizioMorisio}
	\hypertarget{ErionCanoMaurizioMorisio}{} 
	Erion Çano, Maurizio Morisio.
	\textit{\href{https://arxiv.org/abs/1901.03888}{Hybrid Recommender Systems: A Systematic Literature Review}}.
	Intelligent Data Analysis, vol. 21, no. 6, pp. 1487-1524, 2017
	
	\bibitem{datameetsmedia}
	\hypertarget{datameetsmedia}{} 
	An Overview of Recommendation Systems
	\\\texttt{\url{http://datameetsmedia.com/an-overview-of-recommendation-systems/}}
	
	\bibitem{lightfm}
	\hypertarget{lightfm}{} 
	LightFM 1.15 - documentation
	\\\texttt{\url{http://lyst.github.io/lightfm/docs/lightfm.html}}
	
	\bibitem{cs231n}
	\hypertarget{cs231n}{} 
	CS231n: Convolutional Neural Networks for Visual Recognition
	\\\texttt{\url{http://cs231n.stanford.edu/2018/syllabus.html}}
	
	\bibitem{JasonWestonSamyBengioNicolasUsunier}
	\hypertarget{JasonWestonSamyBengioNicolasUsunier}{} 
	Jason Weston, Samy Bengio, Nicolas Usunier.
	\textit{\href{http://www.thespermwhale.com/jaseweston/papers/wsabie-ijcai.pdf}{Wsabie: Scaling up to large vocabulary image annotation}}.
	IJCAI. Vol. 11. 2011.
	
	\bibitem{SteffenRendleChristophFreudenthalerZenoGantnerLarsSchmidtThieme}
	\hypertarget{SteffenRendleChristophFreudenthalerZenoGantnerLarsSchmidtThieme}{} 
	Steffen Rendle, Christoph Freudenthaler, Zeno Gantner and Lars Schmidt-Thieme.
	\textit{\href{http://www.thespermwhale.com/jaseweston/papers/wsabie-ijcai.pdf}{BPR: Bayesian personalized ranking from implicit feedback}}.
	Proceedings of the Twenty-Fifth Conference on Uncertainty in Artificial Intelligence. AUAI Press, 2009.
	
	\bibitem{SimonyanKarenZissermanAndrew}
	\hypertarget{SimonyanKarenZissermanAndrew}{} 
	Karen Simonyan, Andrew Zisserman.
	\textit{\href{https://arxiv.org/pdf/1409.1556.pdf}{Very Deep Convolutional Networks for Large-Scale Image Recognition}}.
	 ICLR, 2015.
	 
	\bibitem{KaimingHeXiangyuZhangShaoqingRenJianSun}
	\hypertarget{KaimingHeXiangyuZhangShaoqingRenJianSun}{} 
	Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun.
	\textit{\href{https://arxiv.org/pdf/1512.03385.pdf}{Deep Residual Learning for Image Recognition}}.
	 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), p770-778, 2016.

	\bibitem{Szegedy2016RethinkingTI}
	\hypertarget{Szegedy2016RethinkingTI}{} 
	Christian Szegedy, Vincent Vanhoucke, Sergey Ioffe, Jonathon Shlens, Zbigniew Wojna.
	\textit{\href{https://arxiv.org/pdf/1512.00567.pdf}{Rethinking the Inception Architecture for Computer Vision}}.
	 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), p2818-2826, 2016.	
	
	\bibitem{Zoph2018LearningTA}
	\hypertarget{Zoph2018LearningTA}{} 
	Barret Zoph, Vijay Vasudevan, Jonathon Shlens, Quoc V. Le.
	\textit{\href{https://arxiv.org/pdf/1707.07012.pdf}{Learning Transferable Architectures for Scalable Image Recognition}}.
	 IEEE/CVF Conference on Computer Vision and Pattern Recognition, p8697-8710, 2018.	
	
	\bibitem{guideinceptionv3}
	\hypertarget{guideinceptionv3}{} 
	Advanced Guide to Inception v3 on Cloud TPU
	\\\texttt{\url{https://cloud.google.com/tpu/docs/inception-v3-advanced}}
	
	\bibitem{dataclusteringtechniques}
	\hypertarget{dataclusteringtechniques}{} 
	Data Clustering Techniques
	\\\texttt{\url{http://www.cs.toronto.edu/~periklis/pubs/depth.pdf}}
	
	\bibitem{gongdeguo}
	\hypertarget{gongdeguo}{} 
	Gongde Guo, Hui Wang, David Bell, Yaxin Bi, Kieran Greer.
	\textit{\href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.2.815&rep=rep1&type=pdf}{KNN Model-Based Approach in Classification}}.
	Lecture Notes in Computer Science, vol 2888. Springer, Berlin, Heidelberg, 2003.

	\bibitem{silhouette}
	\hypertarget{silhouette}{} 
	Sklearn metrics - silhouette score
	\\\texttt{\url{https://scikit-learn.org/stable/modules/generated/sklearn.metrics.silhouette_score.html}}
	
	\bibitem{maciejlightfm}
	\hypertarget{maciejlightfm}{} 
	Maciej Kula
	\textit{\href{https://arxiv.org/pdf/1507.08439.pdf}{Metadata Embeddings for User and Item Cold-start Recommendations}}.
	CoRR abs/1507.08439, 2015.
	
	\bibitem{jasonkos}
	\hypertarget{jasonkos}{} 
	Jason Weston, Hector Yee, Ron J. Weiss.
	\textit{\href{https://static.googleusercontent.com/media/research.google.com/ro//pubs/archive/41534.pdf}{Learning to Rank Recommendations
with the k-Order Statistic Loss}}.
	Proceedings of the 7th ACM conference on Recommender systems. ACM, 2013
	
	\bibitem{ruder2016}
	\hypertarget{ruder2016}{} 
	Sebastian Ruder.
	\textit{\href{http://arxiv.org/abs/1609.04747}{An overview of gradient descent optimization algorithms}}.
	CoRR abs/1609.04747, 2016
	
	\bibitem{lightfm}
	\hypertarget{lightfm}{} 
	Welcome to LightFM’s documentation!
	\\\texttt{\url{http://lyst.github.io/lightfm/docs/home.html}}
	
	\bibitem{movielens}
	\hypertarget{movielens}{} 
	F. Maxwell Harper and Joseph A. Konstan.
	\\\textit{\href{https://doi.org/10.1145/2827872}{The MovieLens Datasets: History and Context.}}
	ACM Transactions on Interactive Intelligent Systems (TiiS) 5, 4: 19:1–19:19.
	
	\bibitem{skopt}
	\hypertarget{skopt}{} 
	skopt API documentation
	\\\texttt{\url{https://scikit-optimize.github.io/}}
	
	\bibitem{themoviedb}
	\hypertarget{themoviedb}{} 
	API Overview - The Movie Database (TMDb)
	\\\texttt{\url{https://www.themoviedb.org/documentation/api}}
\end{thebibliography}
